%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ayad Masud} \\ \vspace{1pt}
    \small 720-453-8040 $|$ \href{mailto:ayad.r.masud@gmail.com}{\underline{ayad.r.masud@gmail.com}} $|$ 
    \href{https://linkedin.com/in/amasud7}{\underline{linkedin.com/in/amasud7/}} $|$
    \href{https://github.com/amasud7}{\underline{github.com/amasud7}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Science in Computer Science, Minor in Statistics: GPA: 3.83}{Aug. 2023 -- Present (Grad: 2027)}
    \resumeSubheading
      {Plano Senior High School}{Plano, TX}
      {GPA: 3.9/4.0}{Aug. 2021 -- May 2023}
  \resumeSubHeadingListEnd


  %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{Languages}{: Python, C++, Java, R, JavaScript, HTML/CSS} \\
    \textbf{Libraries}{: Matplotlib, OpenCV, NumPy, BeautifulSoup, pandas, Selenium, Tensorflow, Flask, Material-UI} \\
    \textbf{Courses}{: Intro to Program Design, Data Structures and Algorithms}
   }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {TAMU RoboMasters Computer Vision Team}{Sept. 2024 - Present}
      {Team Member}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Working in a team to develop computer vision capabilities, such as auto-aim, localization, and icon detection for RoboMasters competition}
        \resumeItem{Built computer vision algorithms to detect numbers on enemy armor plates with a \textbf{90\%} accuracy rate.}
        \resumeItem{Optimized algorithm to compute classification for a frame in \textbf{30ms}, a \textbf{22\%} decrease in computation time compared to previous method.}
      \resumeItemListEnd

    \resumeSubheading
      {Headstarter AI}{July 2024 -- Sept. 2024}
      {Fellow}{Plano, TX}
      \resumeItemListStart
        \resumeItem{Over the course of 7 weeks worked on 5 AI related projects in a team of 4 developers.}
        \resumeItem{Participated in Hiring Hackathon and placed top 20 among 500 teams.}
        \resumeItem{Used Flask, OpenAI, Stripe, Firebase, Clerk, and other technologies to develop full stack web projects.}
        \resumeItem{Received feedback from software engineers, improving code quality, project management, and communication skills}
      \resumeItemListEnd


      \resumeSubheading
      {Aggie Research Scholar Program}{Aug 2024 -- Sept. 2024}
      {Researcher}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Under the guidance of PHD students, worked on insole gait analysis and fall prediction using sensor data.}
        \resumeItem{Cleaned and prepared data for analysis and fed to pose estimation models.}
        \resumeItem{Performed analysis along other team members to detect falls and analyze gait patterns of construction workers.}
      \resumeItemListEnd

      \resumeSubheading
      {CareNow Pharmacy}{May 2024 -- Sept. 2024}
      {Pharmacy Technician}{Plano, TX}
      \resumeItemListStart
        \resumeItem{Utilized pharmacy software systems for data entry tasks, inventory management, and prescription entry}
        \resumeItem{Collaborated with healthcare providers to clarify prescription orders and ensure optimal patient care.}
        \resumeItem{Provided exceptional customer service, addressing patient inquiries regarding prescriptions, dosage instructions, and insurance coverage}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{H.AI.R} $|$ \emph{Python, Flask, Hugging Face, HTML, CSS, Vercel}}{July 2024}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web app to recommend hair care products to users based on their hair type.}
            \resumeItem{Utilized Hugging Face models to classify hair types.}
            \resumeItem{Leveraged Flask framework and Vercel deployment for fully functioning app.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Color Detector} $|$ \emph{OpenCV, Python, Numpy, PIL (Python Imaging Library)}}{May 2024}
          \resumeItemListStart
            \resumeItem{Utilized OpenCV and PIL to develop a Python script to live detect colors in a video feed.}
            \resumeItem{Used Numpy to simultaneously store and manipulate pixel data before detection.}
            \resumeItem{Leveraged PIL's built in bounding box detection to outline regions of colors that are detected.}
            \resumeItem{OpenCV functions were used to perform dilations and masking to easily detect colors.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{LLM Rate My Professor} $|$ \emph{Google Gemini/PaLm API, Python, Selenium, Flask, HTML, CSS}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web app to summarize Rate My Professor reviews.}
            \resumeItem{Utilized Selenium to scrape all reviews for a given professor.}
            \resumeItem{Leveraged Google's Gemini LLM model to summarize scraped reviews into coherent summaries.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%

%-----------Extra-Curricular Activities-----------
%
% \section{Extracurricular}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Aggie Coding Club}{: Took part in weekly meetings, workshops, projects, and social activities} \\
%      \textbf{TAMU Hack}{: Attended several of their hackathons} \\
%      \textbf{Headstarter Hiring Hackathon}{: Participated in weekend hackathons for internship positions.} \\
%     }}
%   \end{itemize}

%-------------------------------------------
\section{Extracurricular}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Aggie Coding Club}{: Took part in weekly meetings, workshops, projects, and social activities} \\
     \textbf{TAMU Hack}{: Attended several of their hackathons} \\
     \textbf{Headstarter Hiring Hackathon}{: Participated in weekend hackathons for internship positions.} \\
    }}
  \end{itemize}

\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{Machine Learning with Python}{: Coursera May 2024} \\
    \textbf{Introduction to Generative AI}{: Google June 2024} \\
    \textbf{Introduction to R}{: DataCamp August 2024} \\
   }}
 \end{itemize}
\end{document}